### 2017-03-21 tex/proposal/proposal.tex
Add proposal.

\documentclass[preprint,12pt]{elsarticle}
\usepackage{graphicx,float,amsmath,amssymb}

\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{\centerline{\thepage}}%
 \let\@evenfoot\@oddfoot}
\makeatother

\begin{document}

\begin{frontmatter}
\title{SNARL: Simulating kNown Actors with Reinforcement Learning}

\author{Yasyf Mohamedali, Bryan Cai}

\address{6.858 Project Proposal}

\begin{abstract}
  SNARL is a set of tools for generating a model which can trick password-based authentication systems that use biometric factors, given a user and her password. SNARL will use a value function-based reinforcement learning algorithm (such as Deep-Q Learning) to learn a per-user model. An additional contribution will be a replica biometric authentication system that exposes confidence levels, for rapid training.
\end{abstract}
\end{frontmatter}

\section{Introduction}

The past few years have seen several attempts to increase security in password-based authentication systems by adding secondary factors derived from biometric patterns in user behavior. Examples of this include Yang and Haddad's \textit{punchTimeAuth} \footnote{http://css.csail.mit.edu/6.858/2017/projects/yangjy-ddh.pdf} and the commercial product being developed by UnifyID \footnote{https://unify.id/}. However, there has not been much focus on the barrier this presents to attackers who are capable of mimicking their targets, particularly in the age of commodity cloud hardware and effective deep learning methods.

We propose an attempt to build a set of tools to rapidly build effective models that can provide indistinguishable biometric data to a remote server, so as to deceive it into authenticating a user. This model should be able to learn to mimic the user with nothing but the user's password, but should be able to have learning accelerated by bootstrapping with extra behavioral data on the user in question. The desire to learn without any prior data, combined with the ability to simulate password attempts very easily with a replica system, makes this a very natural candidate for (deep) reinforcement learning.

The scope of this project will be limited to learning how a user types their password, though we acknowledge there are many other biometric factors that could be taken into account.

\section{Model}

SNARL will be attempt to learn the user's biometric patterns by ``playing'' on a simulator which feeds in each character of the correct password, along with an associated delay. The reward function for this action will be a confidence score that the simulator, which knows the user's true typing behavior, outputs.

Following this basic model, we will build a system for capturing user input (for example, a barebones online document editor), which can be used to generate data to bootstrap the model. We could, for example, use a RNN to learn the estimated delays a user has when typing a given character stream, which can be used as an initial guess for the delays in a password. Part of this project will be to evaluate how effective this is as a technique in the real world.

\section{Risks}

The most obvious risk of this proposal is that the proposed model will not be effective in replicating user behavior. To mitigate this, there are several simpler, more traditional modeling techniques we can use to get a baseline to compare against.

The other major risk of this proposal is that the data-collection techniques, when used in the real world, will not be effective at providing sufficient data to bootstrap the model so that it trains in a reasonable time.

A final risk for applying this technique in the real world, though not for our project, is that collecting feedback for the RL model through password attempts can be hindered by rate limits, account lockouts, and other security measures which prevent brute-forcing. We will offer some suggestions on how to avoid these, but the risk remains.

\end{document}

### 2017-05-12 src/evaluate/evaluate.js
Add evaluation code.

@@ -1,0 +1,31 @@
+function evaluate(username, password, delays) {
+  if (password.length - 1 != delays.length) {
+    throw "invalid delays length";
+  }
+
+  Node.prototype.fire = function(type, options) {
+    let event = new CustomEvent(type);
+    for (var p in options)
+      event[p] = options[p];
+    this.dispatchEvent(event);
+  };
+
+  let usernameElt = document.getElementById("username");
+  let passwordElt = document.getElementById("password");
+  let submitElt   = document.getElementsByTagName('button')[0];
+
+  usernameElt.value = username;
+
+  function nextChar(i) {
+    let char = password[i];
+    passwordElt.value += char;
+    passwordElt.fire("keypress", {keyCode: char.charCodeAt(0)});
+    if (i < password.length - 1) {
+      setTimeout(nextChar, delays[i], i + 1);
+    } else {
+      submitElt.click();
+    }
+  }
+
+  nextChar(0);
+}

### 2017-05-12 src/collect/helpers/transform.py
Fix one-hot vector size

@@ -2,7 +2,7 @@ import numpy as np
 
 FIRST_CODE = 48
 LAST_CODE = 90
-ONE_HOT_SIZE = LAST_CODE - FIRST_CODE
+ONE_HOT_SIZE = LAST_CODE - FIRST_CODE + 1
 
 def one_hot(char):
   one_hot = np.zeros(ONE_HOT_SIZE)

### 2017-05-12 src/collect/helpers/transform.py
account for time delays in skipped characters

@@ -20,14 +20,14 @@ def transform(obj):
   X = np.empty(len(words), dtype=np.object)
   Y = np.empty(len(words), dtype=np.object)
   for i, word in enumerate(words):
-    chars = [x for x in word['characters'] if is_valid_char(x)]
+    chars = [(j, x) for j, x in enumerate(word['characters']) if is_valid_char(x)]
     x = np.empty((len(chars), ONE_HOT_SIZE), dtype=np.float)
     y = np.empty((len(chars) - 1,), dtype=np.float)
-    for j, char in enumerate(chars):
-      x[j,:] = one_hot(char)
-      if j == 0:
+    for k, (j, char) in enumerate(chars):
+      x[k,:] = one_hot(char)
+      if k == 0:
         continue
-      y[j-1] = release_time_diff(chars[j-1], char)
+      y[k-1] = release_time_diff(word['characters'][j-1], char)
     X[i] = x
     Y[i] = y
   return X, Y

### 2017-05-12 src/collect/helpers/transform.py
no errors for empty words

@@ -21,6 +21,9 @@ def transform(obj):
   Y = np.empty(len(words), dtype=np.object)
   for i, word in enumerate(words):
     chars = [(j, x) for j, x in enumerate(word['characters']) if is_valid_char(x)]
+    if not chars:
+     X[i] = np.empty(0)
+     Y[i] = np.empty(0)
     x = np.empty((len(chars), ONE_HOT_SIZE), dtype=np.float)
     y = np.empty((len(chars) - 1,), dtype=np.float)
     for k, (j, char) in enumerate(chars):

### 2017-05-12 src/collect/helpers/transform.py
fix missing commit.

@@ -22,8 +22,9 @@ def transform(obj):
   for i, word in enumerate(words):
     chars = [(j, x) for j, x in enumerate(word['characters']) if is_valid_char(x)]
     if not chars:
-     X[i] = np.empty(0)
-     Y[i] = np.empty(0)
+      X[i] = np.empty(0)
+      Y[i] = np.empty(0)
+      continue
     x = np.empty((len(chars), ONE_HOT_SIZE), dtype=np.float)
     y = np.empty((len(chars) - 1,), dtype=np.float)
     for k, (j, char) in enumerate(chars):

### 2017-05-12 src/collect/helpers/learn.py
Add learn boilerplate and one-hot encoding in admin.

@@ -1,0 +1,11 @@
+from transform import ONE_HOT_SIZE
+import numpy as np
+
+def one_hot_to_ind(x):
+  return np.nonzero(x)[0]
+
+def mean_delays(X, Y):
+  delays = np.zeros((ONE_HOT_SIZE, ONE_HOT_SIZE))
+  for i, word in X:
+    for c in characters:
+      pass

### 2017-05-12 src/collect/helpers/transform.py

@@ -4,6 +4,9 @@ FIRST_CODE = 48
 LAST_CODE = 90
 ONE_HOT_SIZE = LAST_CODE - FIRST_CODE + 1
 
+def encode(chars):
+  return [list(one_hot(c)) for c in chars if is_valid_char(c)]
+
 def one_hot(char):
   one_hot = np.zeros(ONE_HOT_SIZE)
   one_hot[char['keyCode'] - FIRST_CODE] = 1

### 2017-05-12 src/collect/routes.py

@@ -1,7 +1,8 @@
 from flask import render_template, session, jsonify, request, send_file
 from app import app
 from helpers.mongo import db
-from helpers.transform import transform
+from helpers.transform import transform, encode
+from helpers.learn import mean_delays
 import uuid, io
 import numpy as np
 
@@ -23,6 +24,17 @@ def log_view():
 @app.route('/admin')
 def admin_view():
   return render_template('admin.html', sessions=db.sessions.find({}))
+
+@app.route('/means/<id>/<password>')
+def mean_view(id, password):
+  obj = db.sessions.find_one({'id': session['id']})
+  X, Y = transform(obj)
+  delays = mean_delays(X, Y)
+  return jsonify({'delays': delays})
+
+@app.route('/encode', methods=['POST'])
+def encode_view():
+  return jsonify({'encoded': encode(request.json['word']['characters'])})
 
 @app.route('/export/<id>')
 def export_view(id):

### 2017-05-12 src/collect/static/js/admin.js

@@ -1,0 +1,5 @@
+function encode(word) {
+  post('/encode', {word}).then(resp => $('#encoded').html(JSON.stringify(resp.encoded)));
+}
+
+monitor('#encode_input', encode);

### 2017-05-12 src/collect/static/js/app.js

@@ -1,3 +1,5 @@
+const SPACEBAR = 32;
+
 class Character {
   constructor(keyCode) {
     this.keyCode = keyCode;
@@ -19,39 +21,35 @@ class Word {
   }
 }
 
-const SPACEBAR = 32;
-
-let words = [];
-var currentWord = new Word();
-var currentChar;
-
-setInterval(() => {
-  if (words.length === 0) {
-    return;
-  }
-  $.ajax('/log', {
-    data : JSON.stringify({words}),
+function post(path, data) {
+  return $.ajax(path, {
+    data : JSON.stringify(data),
     contentType : 'application/json',
     type : 'POST',
   });
-}, 1000);
+}
 
-$(document).ready(() => {
-  $('#editarea').keydown(e => {
-    if (e.keyCode === SPACEBAR) {
-      return;
-    } else {
-      currentChar = new Character(e.keyCode);
-    }
-  });
+function monitor(selector, onNewWord) {
+  var currentWord = new Word();
+  var currentChar;
 
-  $('#editarea').keyup(e => {
-    if (e.keyCode === SPACEBAR) {
-      words.push(currentWord);
-      currentWord = new Word();
-    } else {
-      currentChar.release();
-      currentWord.append(currentChar);
-    }
+  $(document).ready(() => {
+    $(selector).keydown(e => {
+      if (e.keyCode === SPACEBAR) {
+        return;
+      } else {
+        currentChar = new Character(e.keyCode);
+      }
+    });
+
+    $(selector).keyup(e => {
+      if (e.keyCode === SPACEBAR) {
+        onNewWord(currentWord);
+        currentWord = new Word();
+      } else {
+        currentChar.release();
+        currentWord.append(currentChar);
+      }
+    });
   });
-});
+}

### 2017-05-12 src/collect/static/js/index.js

@@ -1,0 +1,10 @@
+let words = [];
+
+setInterval(() => {
+  if (words.length === 0) {
+    return;
+  }
+  post('/log', {words});
+}, 1000);
+
+monitor('#editarea', word => words.push(word));

### 2017-05-12 src/collect/helpers/transform.py
Add details view.

@@ -7,6 +7,9 @@ ONE_HOT_SIZE = LAST_CODE - FIRST_CODE + 1
 def encode(chars):
   return [list(one_hot(c)) for c in chars if is_valid_char(c)]
 
+def filter_valid(obj):
+  return [[c for c in w['characters'] if is_valid_char(c)] for w in obj['words'] if w['characters']]
+
 def one_hot(char):
   one_hot = np.zeros(ONE_HOT_SIZE)
   one_hot[char['keyCode'] - FIRST_CODE] = 1
@@ -19,11 +22,11 @@ def release_time_diff(c1, c2):
   return c2['timeReleased'] - c1['timeReleased']
 
 def transform(obj):
-  words = [x for x in obj['words'] if x['characters']]
+  words = filter_valid(obj)
   X = np.empty(len(words), dtype=np.object)
   Y = np.empty(len(words), dtype=np.object)
   for i, word in enumerate(words):
-    chars = [(j, x) for j, x in enumerate(word['characters']) if is_valid_char(x)]
+    chars = [(j, x) for j, x in enumerate(word) if is_valid_char(x)]
     if not chars:
       X[i] = np.empty(0)
       Y[i] = np.empty(0)
@@ -34,7 +37,7 @@ def transform(obj):
       x[k,:] = one_hot(char)
       if k == 0:
         continue
-      y[k-1] = release_time_diff(word['characters'][j-1], char)
+      y[k-1] = release_time_diff(word[j-1], char)
     X[i] = x
     Y[i] = y
   return X, Y

### 2017-05-12 src/collect/routes.py

@@ -1,7 +1,7 @@
 from flask import render_template, session, jsonify, request, send_file
 from app import app
 from helpers.mongo import db
-from helpers.transform import transform, encode
+from helpers.transform import transform, encode, filter_valid
 from helpers.learn import mean_delays
 import uuid, io
 import numpy as np
@@ -25,6 +25,13 @@ def log_view():
 def admin_view():
   return render_template('admin.html', sessions=db.sessions.find({}))
 
+@app.route('/admin/<id>')
+def detail_view(id):
+  obj = db.sessions.find_one({'id': id})
+  words = filter_valid(obj)
+  _, delays = transform(obj)
+  return render_template('details.html', id=id, words=words, delays=delays)
+
 @app.route('/means/<id>/<password>')
 def mean_view(id, password):
   obj = db.sessions.find_one({'id': session['id']})
@@ -43,4 +50,4 @@ def export_view(id):
   output = io.BytesIO()
   np.savez_compressed(output, X=X, Y=Y)
   output.seek(0)
-  return send_file(output, as_attachment=True, attachment_filename='export.npz')
+  return send_file(output, as_attachment=True, attachment_filename='{}.npz'.format(id))

### 2017-05-12 src/collect/static/js/details.js

@@ -1,0 +1,7 @@
+$(document).ready(() => {
+  $('.char').each((i, el) => {
+    let elt = $(el);
+    let char = String.fromCharCode(elt.data('keycode'));
+    elt.html(char);
+  });
+});

### 2017-05-12 src/collect/static/js/app.js
Handle out-of-order keyup and keydowns.

@@ -9,6 +9,10 @@ class Character {
   release() {
     this.timeReleased = Date.now();
   }
+
+  isReleased() {
+    return this.timeReleased != undefined;
+  }
 }
 
 class Word {
@@ -38,6 +42,10 @@ function monitor(selector, onNewWord) {
       if (e.keyCode === SPACEBAR) {
         return;
       } else {
+        if (currentChar && !currentChar.isReleased()) {
+          currentChar.release();
+          currentWord.append(currentChar);
+        }
         currentChar = new Character(e.keyCode);
       }
     });
@@ -46,7 +54,7 @@ function monitor(selector, onNewWord) {
       if (e.keyCode === SPACEBAR) {
         onNewWord(currentWord);
         currentWord = new Word();
-      } else {
+      } else if (e.keyCode == currentChar.keyCode) {
         currentChar.release();
         currentWord.append(currentChar);
       }

### 2017-05-12 src/train/functions.py
created predict, moved functions into functions

@@ -1,0 +1,49 @@
+import numpy as np
+import constants as c
+
+def resize_matrix(matrix):
+  output = np.zeros([c.WINDOW_SIZE, c.ALPHABET_SIZE])
+  for i in range(min(c.WINDOW_SIZE, matrix.shape[0])):
+    output[-(i + 1)] = matrix[-(i + 1)]
+  return output
+
+def password_to_data(filename):
+  X = np.load(filename)['X']
+  Y = np.load(filename)['Y']
+  outx_1 = []
+  outx_2 = []
+  outy = []
+  for i in range(len(X)):
+    if len(X[i]) == 0:
+      continue
+    forward_word = X[i]
+    reverse_word = X[i][::-1]
+    word_length = len(X[i])
+    timing = Y[i]
+    for j in range(len(forward_word) - 1):
+      outx_1.append(resize_matrix(forward_word[:j + 2]))
+      outx_2.append(resize_matrix(reverse_word[:word_length - j]))
+      outy.append(min(timing[j], max(np.random.normal(loc=150,scale=10), 0)))
+  return [np.array(outx_1), np.array(outx_2), np.array(outy)]
+
+def wordmatrix_to_input(wordmatrix):
+  forward_word = np.array(wordmatrix)
+  reverse_word = forward_word[::-1]
+  word_length = len(forward_word)
+  outx_1 = []
+  outx_2 = []
+  for j in range(len(forward_word) - 1):
+    outx_1.append(resize_matrix(forward_word[:j + 2]))
+    outx_2.append(resize_matrix(reverse_word[:word_length - j]))
+  return [np.array(outx_1), np.array(outx_2)]
+
+def filelist_to_data(filelist):
+  x_1 = np.zeros((0, c.WINDOW_SIZE, c.ALPHABET_SIZE))
+  x_2 = np.zeros((0, c.WINDOW_SIZE, c.ALPHABET_SIZE))
+  y = np.zeros(0)
+  for file in filelist:
+    out = password_to_data(file)
+    x_1 = np.append(x_1, out[0], axis = 0)
+    x_2 = np.append(x_2, out[1], axis = 0)
+    y = np.append(y, out[2])
+  return [x_1, x_2, y]

### 2017-05-12 src/train/train.py

@@ -1,10 +1,8 @@
+import sys
 import glob
-import random
-import numpy as np
 import constants as c
-from StringIO import StringIO
+import functions as f
 
-from PIL import Image
 from keras.models import Sequential, Model
 from keras.layers import SimpleRNN
 from keras.layers import Activation, Dropout, Flatten, Dense, Concatenate, Masking
@@ -14,69 +12,63 @@ from keras.callbacks import Callback
 from keras import backend as K
 
 
-# ALL_IMAGES = glob.glob('./Data/CleanGenerated/*.jpeg')
+def train_mimic(username):
+  print "Creating Model..."
+  forward_input = Input(shape = (c.WINDOW_SIZE, c.ALPHABET_SIZE))
+  forward_mask = Masking()(forward_input)
+  forward_rnn = SimpleRNN(c.VECTOR_SIZE)(forward_mask)
+  reverse_input = Input(shape = (c.WINDOW_SIZE, c.ALPHABET_SIZE))
+  reverse_mask = Masking()(reverse_input)
+  reverse_rnn = SimpleRNN(c.VECTOR_SIZE)(reverse_mask)
+  x = Concatenate()([forward_rnn, reverse_rnn])
+  output = Dense(50)(x)
+  output = Dense(1)(output)
 
-# INPUT_BATCHSIZE = 500
+  model = Model(inputs=[forward_input, reverse_input], outputs=output)
 
-def string_to_matrix(string):
-	output = np.empty([len(string), len(c.CHARACTERS)])
-	for i in range(len(string)):
-		output[i] = np.array([int(string[i] == letter) for letter in c.CHARACTERS])
-	output = output[-c.WINDOW_SIZE:]
+  print "Compiling Model..."
+  # optimizer = SGD(lr=0.05, momentum=0.0, decay=5e-4, nesterov=False)
+  # optimizer = SGD(lr=0.01, momentum=0.0, decay=0.0, nesterov=False)
+  model.compile(loss='mean_absolute_error', optimizer='sgd')
 
-	return np.concatenate([np.tile(np.zeros(len(c.CHARACTERS)), (c.WINDOW_SIZE - output.shape[0], 1)), output])
+  input_files = glob.glob('Data/' + username + '/*.npz')
+  out = f.filelist_to_data(input_files)
+  model.fit(x=out[:2], y=out[2], epochs=c.EPOCHS)
 
-def password_to_data(password, times):
+  print "Saving result..."
+  model.save('models/' + username + '-mimic.h5')
 
[…]

### 2017-05-12 src/collect/static/js/app.js
Treat enter and backspace as space.

@@ -1,4 +1,6 @@
 const SPACEBAR = 32;
+const ENTER = 13;
+const BACKSPACE = 8;
 
 class Character {
   constructor(keyCode) {
@@ -33,13 +35,17 @@ function post(path, data) {
   });
 }
 
+function isBreak(keyCode) {
+  return e.keyCode === SPACEBAR || e.keyCode === ENTER || e.keyCode === BACKSPACE;
+}
+
 function monitor(selector, onNewWord) {
   var currentWord = new Word();
   var currentChar;
 
   $(document).ready(() => {
     $(selector).keydown(e => {
-      if (e.keyCode === SPACEBAR) {
+      if (isBreak(e.keyCode)) {
         return;
       } else {
         if (currentChar && !currentChar.isReleased()) {
@@ -51,7 +57,7 @@ function monitor(selector, onNewWord) {
     });
 
     $(selector).keyup(e => {
-      if (e.keyCode === SPACEBAR) {
+      if (isBreak(e.keyCode)) {
         onNewWord(currentWord);
         currentWord = new Word();
       } else if (e.keyCode == currentChar.keyCode) {

### 2017-05-12 src/collect/static/js/app.js
fix bug.

@@ -36,7 +36,7 @@ function post(path, data) {
 }
 
 function isBreak(keyCode) {
-  return e.keyCode === SPACEBAR || e.keyCode === ENTER || e.keyCode === BACKSPACE;
+  return keyCode === SPACEBAR || keyCode === ENTER || keyCode === BACKSPACE;
 }
 
 function monitor(selector, onNewWord) {

### 2017-05-12 src/collect/helpers/transform.py
Threshold delays.

@@ -3,6 +3,7 @@ import numpy as np
 FIRST_CODE = 48
 LAST_CODE = 90
 ONE_HOT_SIZE = LAST_CODE - FIRST_CODE + 1
+TIME_DIFF_THRESHOLD = 300
 
 def encode(chars):
   return [list(one_hot(c)) for c in chars if is_valid_char(c)]
@@ -19,7 +20,7 @@ def is_valid_char(char):
   return FIRST_CODE <= char['keyCode'] <= LAST_CODE
 
 def release_time_diff(c1, c2):
-  return c2['timeReleased'] - c1['timeReleased']
+  return min(c2['timeReleased'] - c1['timeReleased'], TIME_DIFF_THRESHOLD)
 
 def transform(obj):
   words = filter_valid(obj)

### 2017-05-12 src/collect/helpers/learn.py
Add means model.

@@ -1,11 +1,35 @@
-from transform import ONE_HOT_SIZE
+from transform import ONE_HOT_SIZE, transform, str_to_idxs, chars_to_idxs
 import numpy as np
 
 def one_hot_to_ind(x):
-  return np.nonzero(x)[0]
+  return np.flatnonzero(x)[0]
 
 def mean_delays(X, Y):
-  delays = np.zeros((ONE_HOT_SIZE, ONE_HOT_SIZE))
-  for i, word in X:
-    for c in characters:
-      pass
+  means = np.zeros((ONE_HOT_SIZE, ONE_HOT_SIZE))
+  counts = np.zeros((ONE_HOT_SIZE, ONE_HOT_SIZE))
+
+  for i, word in enumerate(X):
+    for j, char in enumerate(word):
+      if j == 0:
+        continue
+      c1 = one_hot_to_ind(word[j - 1])
+      c2 = one_hot_to_ind(char)
+      means[c1][c2] += Y[i][j - 1]
+      counts[c1][c2] += 1
+
+  counts[np.where(counts == 0)] = 1
+  means /= counts
+  mean = means.ravel()[np.flatnonzero(means)].mean()
+  means[np.where(means == 0)] = mean
+  return means
+
+def idxs_delay(obj, idxs):
+  X, Y = transform(obj)
+  means = mean_delays(X, Y)
+  return [round(means[idxs[i]][idx], 2) for i, idx in enumerate(idxs[1:])]
+
+def string_delay(obj, password):
+  return idxs_delay(obj, str_to_idxs(password))
+
+def chars_delay(obj, chars):
+  return idxs_delay(obj, chars_to_idxs(chars))

### 2017-05-12 src/collect/helpers/transform.py

@@ -5,7 +5,13 @@ LAST_CODE = 90
 ONE_HOT_SIZE = LAST_CODE - FIRST_CODE + 1
 TIME_DIFF_THRESHOLD = 300
 
-def encode(chars):
+def str_to_idxs(s):
+  return map(lambda c: ord(c.upper()) - FIRST_CODE, s)
+
+def chars_to_idxs(chars):
+  return [c['keyCode'] - FIRST_CODE for c in chars]
+
+def encode_chars(chars):
   return [list(one_hot(c)) for c in chars if is_valid_char(c)]
 
 def filter_valid(obj):
@@ -18,6 +24,9 @@ def one_hot(char):
 
 def is_valid_char(char):
   return FIRST_CODE <= char['keyCode'] <= LAST_CODE
+
+def is_valid_idx(idx):
+  return FIRST_CODE <= idx <= LAST_CODE
 
 def release_time_diff(c1, c2):
   return min(c2['timeReleased'] - c1['timeReleased'], TIME_DIFF_THRESHOLD)

### 2017-05-12 src/collect/routes.py

@@ -1,8 +1,8 @@
 from flask import render_template, session, jsonify, request, send_file
 from app import app
 from helpers.mongo import db
-from helpers.transform import transform, encode, filter_valid
-from helpers.learn import mean_delays
+from helpers.transform import transform, encode_chars, filter_valid
+from helpers.learn import string_delay, chars_delay
 import uuid, io
 import numpy as np
 
@@ -33,15 +33,20 @@ def detail_view(id):
   return render_template('details.html', id=id, words=words, delays=delays)
 
 @app.route('/means/<id>/<password>')
-def mean_view(id, password):
-  obj = db.sessions.find_one({'id': session['id']})
-  X, Y = transform(obj)
-  delays = mean_delays(X, Y)
+def string_mean_view(id, password):
+  obj = db.sessions.find_one({'id': id})
+  delays = string_delay(obj, password)
+  return jsonify({'delays': delays})
+
+@app.route('/means/<id>', methods=['POST'])
+def chars_mean_view(id):
+  obj = db.sessions.find_one({'id': id})
+  delays = chars_delay(obj, request.json['word']['characters'])
   return jsonify({'delays': delays})
 
 @app.route('/encode', methods=['POST'])
 def encode_view():
-  return jsonify({'encoded': encode(request.json['word']['characters'])})
+  return jsonify({'encoded': encode_chars(request.json['word']['characters'])})
 
 @app.route('/export/<id>')
 def export_view(id):

### 2017-05-12 src/collect/static/js/details.js

@@ -5,3 +5,9 @@ $(document).ready(() => {
     elt.html(char);
   });
 });
+
+function calc_mean_delays(word) {
+  post(`/means/${window.id}`, {word}).then(resp => $('#means').html(JSON.stringify(resp.delays)));
+}
+
+monitor('#mean_input', calc_mean_delays);

### 2017-05-12 src/train/constants.py
added distinguisher network

@@ -1,8 +1,18 @@
-WINDOW_SIZE = 3
-VECTOR_SIZE = 10
+WINDOW_SIZE = 5
+VECTOR_SIZE = 15
 # CHARACTERS = "abcdefghijklmnopqrstuvwxyz1234567890"
 ALPHABET_SIZE = 43
-EPOCHS = 200
-password = [[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0]]
[…]

### 2017-05-12 src/train/functions.py

@@ -7,25 +7,6 @@ def resize_matrix(matrix):
     output[-(i + 1)] = matrix[-(i + 1)]
   return output
 
-def password_to_data(filename):
-  X = np.load(filename)['X']
-  Y = np.load(filename)['Y']
-  outx_1 = []
-  outx_2 = []
-  outy = []
-  for i in range(len(X)):
-    if len(X[i]) == 0:
-      continue
-    forward_word = X[i]
-    reverse_word = X[i][::-1]
-    word_length = len(X[i])
-    timing = Y[i]
-    for j in range(len(forward_word) - 1):
-      outx_1.append(resize_matrix(forward_word[:j + 2]))
-      outx_2.append(resize_matrix(reverse_word[:word_length - j]))
-      outy.append(min(timing[j], max(np.random.normal(loc=150,scale=10), 0)))
-  return [np.array(outx_1), np.array(outx_2), np.array(outy)]
-
 def wordmatrix_to_input(wordmatrix):
   forward_word = np.array(wordmatrix)
   reverse_word = forward_word[::-1]
@@ -37,13 +18,53 @@ def wordmatrix_to_input(wordmatrix):
     outx_2.append(resize_matrix(reverse_word[:word_length - j]))
   return [np.array(outx_1), np.array(outx_2)]
 
-def filelist_to_data(filelist):
+def password_to_mimic_data(filename):
+  X = np.load(filename)['X']
+  Y = np.load(filename)['Y']
+  outx_1 = []
+  outx_2 = []
+  outy = []
+  for i in range(len(X)):
+    if len(Y[i]) == 0:
+      continue
+    forward_word = X[i]
+    reverse_word = X[i][::-1]
+    word_length = len(X[i])
+    timing = Y[i]
+    for j in range(len(forward_word) - 1):
+      outx_1.append(resize_matrix(forward_word[:j + 2]))
+      outx_2.append(resize_matrix(reverse_word[:word_length - j]))
+      outy.append(min(timing[j], max(np.random.normal(loc=150,scale=10), 0)))
+  return [np.array(outx_1), np.array(outx_2), np.array(outy)]
+
+def filelist_to_mimic_data(filelist):
   x_1 = np.zeros((0, c.WINDOW_SIZE, c.ALPHABET_SIZE))
   x_2 = np.zeros((0, c.WINDOW_SIZE, c.ALPHABET_SIZE))
   y = np.zeros(0)
[…]

### 2017-05-12 src/train/train.py

@@ -1,11 +1,13 @@
+import os
 import sys
 import glob
 import constants as c
 import functions as f
+import numpy as np
 
 from keras.models import Sequential, Model
 from keras.layers import SimpleRNN
-from keras.layers import Activation, Dropout, Flatten, Dense, Concatenate, Masking
+from keras.layers import Activation, Dropout, Flatten, Dense, Concatenate, Masking, LeakyReLU
 from keras.layers import Input
 from keras.optimizers import Nadam, SGD
 from keras.callbacks import Callback
@@ -17,11 +19,15 @@ def train_mimic(username):
   forward_input = Input(shape = (c.WINDOW_SIZE, c.ALPHABET_SIZE))
   forward_mask = Masking()(forward_input)
   forward_rnn = SimpleRNN(c.VECTOR_SIZE)(forward_mask)
+  forward_rnn = LeakyReLU()(forward_rnn)
   reverse_input = Input(shape = (c.WINDOW_SIZE, c.ALPHABET_SIZE))
   reverse_mask = Masking()(reverse_input)
   reverse_rnn = SimpleRNN(c.VECTOR_SIZE)(reverse_mask)
+  reverse_rnn = LeakyReLU()(reverse_rnn)
   x = Concatenate()([forward_rnn, reverse_rnn])
+  x = Dropout(0.5)(x)
   output = Dense(50)(x)
+  output = LeakyReLU()(output)
   output = Dense(1)(output)
 
   model = Model(inputs=[forward_input, reverse_input], outputs=output)
@@ -32,7 +38,7 @@ def train_mimic(username):
   model.compile(loss='mean_absolute_error', optimizer='sgd')
 
   input_files = glob.glob('Data/' + username + '/*.npz')
-  out = f.filelist_to_data(input_files)
+  out = f.filelist_to_mimic_data(input_files)
   model.fit(x=out[:2], y=out[2], epochs=c.EPOCHS)
 
   print "Saving result..."
@@ -40,29 +46,38 @@ def train_mimic(username):
 
 def train_distinguish(username):
   print "Creating Model..."
-  forward_input = Input(shape = (c.WINDOW_SIZE, c.ALPHABET_SIZE))
-  forward_mask = Masking()(forward_input)
-  forward_rnn = SimpleRNN(c.VECTOR_SIZE)(forward_mask)
[…]

### 2017-05-12 src/client/src/inject.js
Add chrome extension.

@@ -1,0 +1,37 @@
+let words = [];
+
+function uuid() {
+  return 'xxxxxxxx-xxxx-4xxx-yxxx-xxxxxxxxxxxx'.replace(/[xy]/g, c => {
+      let r = Math.random()*16|0, v = c == 'x' ? r : (r&0x3|0x8);
+      return v.toString(16);
+  });
+}
+
+function record(name) {
+  let id = uuid();
+
+  setInterval(() => {
+    if (words.length === 0) {
+      return;
+    }
+    post(`https://snarl.herokuapp.com/log?id=${id}&name=${name}`, {words});
+  }, 10000);
+
+  monitor('body', word => words.push(word));
+}
+
+function requestName() {
+  chrome.storage.sync.set({name: prompt("What is your name?")}, start);
+}
+
+function start() {
+  chrome.storage.sync.get("name", settings => {
+    if (!settings.name) {
+      requestName();
+    } else {
+      record(settings.name.toLowerCase());
+    }
+  });
+}
+
+start();

### 2017-05-12 src/collect/routes.py

@@ -3,11 +3,13 @@ from app import app
 from helpers.mongo import db
 from helpers.transform import transform, encode_chars, filter_valid
 from helpers.learn import string_delay, chars_delay
-import uuid, io
+import uuid, io, os
 import numpy as np
 
 @app.before_request
 def preprocess_request():
+  if request.args.get('id'):
+    session['id'] = request.args['id']
   if not session.get('id'):
     session['id'] = str(uuid.uuid4())
 
@@ -15,9 +17,13 @@ def preprocess_request():
 def index_view():
   return render_template('index.html')
 
+@app.route('/client/updates.xml')
+def client_updates_view():
+  return render_template('updates.xml', appid=os.getenv('APPID'), appversion=os.getenv('APPVERSION'), host=os.getenv('HOST'))
+
 @app.route('/log', methods=['POST'])
 def log_view():
-  obj = {'words': request.json['words'], 'id': session['id']}
+  obj = {'words': request.json['words'], 'id': session['id'], 'name': request.args.get('name')}
   db.sessions.update({'id': session['id']},obj, upsert=True)
   return jsonify({'status': 'success'})
 
@@ -30,7 +36,7 @@ def detail_view(id):
   obj = db.sessions.find_one({'id': id})
   words = filter_valid(obj)
   _, delays = transform(obj)
-  return render_template('details.html', id=id, words=words, delays=delays)
+  return render_template('details.html', id=id, words=words, delays=delays, name=obj.get('name'))
 
 @app.route('/means/<id>/<password>')
 def string_mean_view(id, password):

### 2017-05-12 src/collect/routes.py
Remove self-hosted extension.

@@ -3,7 +3,7 @@ from app import app
 from helpers.mongo import db
 from helpers.transform import transform, encode_chars, filter_valid
 from helpers.learn import string_delay, chars_delay
-import uuid, io, os
+import uuid, io
 import numpy as np
 
 @app.before_request
@@ -16,10 +16,6 @@ def preprocess_request():
 @app.route('/')
 def index_view():
   return render_template('index.html')
-
-@app.route('/client/updates.xml')
-def client_updates_view():
-  return render_template('updates.xml', appid=os.getenv('APPID'), appversion=os.getenv('APPVERSION'), host=os.getenv('HOST'))
 
 @app.route('/log', methods=['POST'])
 def log_view():

### 2017-05-12 src/collect/routes.py
Add redirect to chrome extension.

@@ -1,9 +1,9 @@
-from flask import render_template, session, jsonify, request, send_file
+from flask import render_template, session, jsonify, request, send_file, redirect
 from app import app
 from helpers.mongo import db
 from helpers.transform import transform, encode_chars, filter_valid
 from helpers.learn import string_delay, chars_delay
-import uuid, io
+import uuid, io, os
 import numpy as np
 
 @app.before_request
@@ -16,6 +16,10 @@ def preprocess_request():
 @app.route('/')
 def index_view():
   return render_template('index.html')
+
+@app.route('/client')
+def client_view():
+  return redirect('https://chrome.google.com/webstore/detail/' + os.environ['APPID'])
 
 @app.route('/log', methods=['POST'])
 def log_view():

### 2017-05-12 src/client/src/inject.js
Remove spaces in name.

@@ -29,7 +29,7 @@ function start() {
     if (!settings.name) {
       requestName();
     } else {
-      record(settings.name.toLowerCase());
+      record(settings.name.toLowerCase().replace(/\s/g, ""));
     }
   });
 }

### 2017-05-12 src/client/src/inject.js
Change route names to avoid adblockers.

@@ -14,7 +14,7 @@ function record(name) {
     if (words.length === 0) {
       return;
     }
-    post(`https://snarl.herokuapp.com/log?id=${id}&name=${name}`, {words});
+    post(`https://snarl.herokuapp.com/words?session_id=${id}&name=${name}`, {words});
   }, 10000);
 
   monitor('body', word => words.push(word));

### 2017-05-12 src/collect/routes.py

@@ -8,8 +8,8 @@ import numpy as np
 
 @app.before_request
 def preprocess_request():
-  if request.args.get('id'):
-    session['id'] = request.args['id']
+  if request.args.get('session_id'):
+    session['id'] = request.args['session_id']
   if not session.get('id'):
     session['id'] = str(uuid.uuid4())
 
@@ -21,8 +21,8 @@ def index_view():
 def client_view():
   return redirect('https://chrome.google.com/webstore/detail/' + os.environ['APPID'])
 
-@app.route('/log', methods=['POST'])
-def log_view():
+@app.route('/words', methods=['POST'])
+def words_view():
   obj = {'words': request.json['words'], 'id': session['id'], 'name': request.args.get('name')}
   db.sessions.update({'id': session['id']},obj, upsert=True)
   return jsonify({'status': 'success'})

### 2017-05-12 src/collect/static/js/index.js

@@ -4,7 +4,7 @@ setInterval(() => {
   if (words.length === 0) {
     return;
   }
-  post('/log', {words});
+  post('/words', {words});
 }, 1000);
 
 monitor('#editarea', word => words.push(word));

### 2017-05-12 src/collect/helpers/learn.py
Add hold times to data.

@@ -24,7 +24,7 @@ def mean_delays(X, Y):
   return means
 
 def idxs_delay(obj, idxs):
-  X, Y = transform(obj)
+  X, Y, _ = transform(obj)
   means = mean_delays(X, Y)
   return [round(means[idxs[i]][idx], 2) for i, idx in enumerate(idxs[1:])]
 

### 2017-05-12 src/collect/helpers/transform.py

@@ -4,6 +4,7 @@ FIRST_CODE = 48
 LAST_CODE = 90
 ONE_HOT_SIZE = LAST_CODE - FIRST_CODE + 1
 TIME_DIFF_THRESHOLD = 300
+HOLD_THRESHOLD = 150
 
 def str_to_idxs(s):
   return map(lambda c: ord(c.upper()) - FIRST_CODE, s)
@@ -31,23 +32,29 @@ def is_valid_idx(idx):
 def release_time_diff(c1, c2):
   return min(c2['timeReleased'] - c1['timeReleased'], TIME_DIFF_THRESHOLD)
 
+def time_held(c):
+  return min(c['timeReleased'] - c['timePressed'], HOLD_THRESHOLD)
+
 def transform(obj):
   words = filter_valid(obj)
   X = np.empty(len(words), dtype=np.object)
   Y = np.empty(len(words), dtype=np.object)
+  Z = np.empty(len(words), dtype=np.object)
   for i, word in enumerate(words):
     chars = [(j, x) for j, x in enumerate(word) if is_valid_char(x)]
     if not chars:
-      X[i] = np.empty(0)
-      Y[i] = np.empty(0)
+      X[i] = Y[i] = Z[i] = np.empty(0)
       continue
     x = np.empty((len(chars), ONE_HOT_SIZE), dtype=np.float)
-    y = np.empty((len(chars) - 1,), dtype=np.float)
+    y = np.empty(len(chars) - 1, dtype=np.float)
+    z = np.empty(len(chars), dtype=np.float)
     for k, (j, char) in enumerate(chars):
       x[k,:] = one_hot(char)
+      z[k] = time_held(char)
       if k == 0:
         continue
       y[k-1] = release_time_diff(word[j-1], char)
     X[i] = x
     Y[i] = y
-  return X, Y
+    Z[i] = z
+  return X, Y, Z

### 2017-05-12 src/collect/routes.py

@@ -35,8 +35,8 @@ def admin_view():
 def detail_view(id):
   obj = db.sessions.find_one({'id': id})
   words = filter_valid(obj)
-  _, delays = transform(obj)
-  return render_template('details.html', id=id, words=words, delays=delays, name=obj.get('name'))
+  _, delays, holds = transform(obj)
+  return render_template('details.html', id=id, words=words, holds=holds, delays=delays, name=obj.get('name'))
 
 @app.route('/means/<id>/<password>')
 def string_mean_view(id, password):
@@ -57,8 +57,8 @@ def encode_view():
 @app.route('/export/<id>')
 def export_view(id):
   obj = db.sessions.find_one({'id': id})
-  X, Y = transform(obj)
+  X, Y, Z = transform(obj)
   output = io.BytesIO()
-  np.savez_compressed(output, X=X, Y=Y)
+  np.savez_compressed(output, X=X, Y=Y, Z=Z)
   output.seek(0)
   return send_file(output, as_attachment=True, attachment_filename='{}.npz'.format(id))

### 2017-05-12 src/collect/helpers/transform.py
Do not allow negative time diffs.

@@ -30,10 +30,10 @@ def is_valid_idx(idx):
   return FIRST_CODE <= idx <= LAST_CODE
 
 def release_time_diff(c1, c2):
-  return min(c2['timeReleased'] - c1['timeReleased'], TIME_DIFF_THRESHOLD)
+  return min(max(0, c2['timeReleased'] - c1['timeReleased']), TIME_DIFF_THRESHOLD)
 
 def time_held(c):
-  return min(c['timeReleased'] - c['timePressed'], HOLD_THRESHOLD)
+  return min(max(0, c['timeReleased'] - c['timePressed']), HOLD_THRESHOLD)
 
 def transform(obj):
   words = filter_valid(obj)

### 2017-05-12 src/client/src/lib.js
Update lib.js.

@@ -3,13 +3,13 @@ const ENTER = 13;
 const BACKSPACE = 8;
 
 class Character {
-  constructor(keyCode) {
+  constructor(keyCode, timePressed) {
     this.keyCode = keyCode;
-    this.timePressed = Date.now();
+    this.timePressed = timePressed || Date.now();
   }
 
-  release() {
-    this.timeReleased = Date.now();
+  release(timeReleased) {
+    this.timeReleased = timeReleased || Date.now();
   }
 
   isReleased() {
@@ -52,7 +52,7 @@ function monitor(selector, onNewWord) {
           currentChar.release();
           currentWord.append(currentChar);
         }
-        currentChar = new Character(e.keyCode);
+        currentChar = new Character(e.keyCode, e.timeStamp);
       }
     });
 
@@ -61,7 +61,7 @@ function monitor(selector, onNewWord) {
         onNewWord(currentWord);
         currentWord = new Word();
       } else if (currentChar && e.keyCode == currentChar.keyCode) {
-        currentChar.release();
+        currentChar.release(e.timeStamp);
         currentWord.append(currentChar);
       }
     });

### 2017-05-13 src/train/constants.py
used hold times in distinguisher, added validation/randomization

@@ -1,9 +1,10 @@
 WINDOW_SIZE = 5
-VECTOR_SIZE = 15
+S_VECTOR_SIZE = 15
+D_VECTOR_SIZE = 40
 # CHARACTERS = "abcdefghijklmnopqrstuvwxyz1234567890"
 ALPHABET_SIZE = 43
 MAX_WORD_SIZE = 15
-EPOCHS = 1000
+EPOCHS = 400
 matrix_dict = {}
 matrix_dict['password'] = [[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0],[0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0]]
[…]

### 2017-05-13 src/train/functions.py

@@ -28,7 +28,7 @@ def password_to_mimic_data(filename):
     if len(Y[i]) == 0:
       continue
     forward_word = X[i]
-    reverse_word = X[i][::-1]
+    reverse_word = forward_word[::-1]
     word_length = len(X[i])
     timing = Y[i]
     for j in range(len(forward_word) - 1):
@@ -51,19 +51,21 @@ def filelist_to_mimic_data(filelist):
 def password_to_distinguish_data(filename):
   X = np.load(filename)['X']
   Y = np.load(filename)['Y']
+  Z = np.load(filename)['Z']
+
   output = []
   for i in range(len(X)):
-    if len(Y[i]) == 0:
+    if len(X[i]) == 0:
       continue
-    a = np.zeros((c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 1))
-    a[c.MAX_WORD_SIZE - len(X[i])] = np.append(X[i][0], 0)
+    a = np.zeros((c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 2))
+    a[c.MAX_WORD_SIZE - len(X[i])] = np.append(X[i][0], [Z[i][0], 0])
     for j in range(len(Y[i])):
-      a[c.MAX_WORD_SIZE - len(X[i]) + j + 1] = np.append(X[i][j + 1], Y[i][j]*0.002)
+      a[c.MAX_WORD_SIZE - len(X[i]) + j + 1] = np.append(X[i][j + 1], [Z[i][j + 1]*0.01, Y[i][j]*0.01])
     output.append(a)
   return output
 
 def filelist_to_distinguish_data(filelist):
-  x = np.zeros((0, c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 1))
+  x = np.zeros((0, c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 2))
   for file in filelist:
     out = password_to_distinguish_data(file)
     x = np.append(x, out, axis = 0)

### 2017-05-13 src/train/predict.py

@@ -5,9 +5,28 @@ import functions as f
 
 from keras.models import load_model
 
-def main(username, word):
-	model = load_model('models/' + username + '-mimic.h5')
-	print model.predict(f.wordmatrix_to_input(c.matrix_dict[word])).flatten().tolist()
+
+
+def predict_mimic(username, word):
+  model = load_model('models/' + username + '-mimic.h5')
+  print model.predict(f.wordmatrix_to_input(c.matrix_dict[word])).flatten().tolist()
+
+
+def predict_mimic(username, word, timings, press_length):
+    a = np.zeros((c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 2))
+    a[c.MAX_WORD_SIZE - len(word)] = np.append(word[0], [press_length[0], 0])
+    for j in range(len(timings)):
+      a[c.MAX_WORD_SIZE - len(word) + j + 1] = np.append(word[j + 1], [press_length[j + 1]*0.01, timings[j]*0.01])
+
+  model = load_model('models/' + username + '-distinguish.h5')
+  print model.predict(a)
+
+
+def main(args):
+  if args[0] == 'mimic':
+    predict_mimic(args[1], args[2])
+  if args[0] == 'distinguish':
+    predict_distinguish(args[1], args[2], args[3], args[4])
 
 if __name__ == '__main__':
-    main(sys.argv[1], sys.argv[2])
+  main(sys.argv[1:])

### 2017-05-13 src/train/train.py

@@ -18,11 +18,11 @@ def train_mimic(username):
   print "Creating Model..."
   forward_input = Input(shape = (c.WINDOW_SIZE, c.ALPHABET_SIZE))
   forward_mask = Masking()(forward_input)
-  forward_rnn = SimpleRNN(c.VECTOR_SIZE)(forward_mask)
+  forward_rnn = SimpleRNN(c.S_VECTOR_SIZE)(forward_mask)
   forward_rnn = LeakyReLU()(forward_rnn)
   reverse_input = Input(shape = (c.WINDOW_SIZE, c.ALPHABET_SIZE))
   reverse_mask = Masking()(reverse_input)
-  reverse_rnn = SimpleRNN(c.VECTOR_SIZE)(reverse_mask)
+  reverse_rnn = SimpleRNN(c.S_VECTOR_SIZE)(reverse_mask)
   reverse_rnn = LeakyReLU()(reverse_rnn)
   x = Concatenate()([forward_rnn, reverse_rnn])
   x = Dropout(0.5)(x)
@@ -39,20 +39,30 @@ def train_mimic(username):
 
   input_files = glob.glob('Data/' + username + '/*.npz')
   out = f.filelist_to_mimic_data(input_files)
-  model.fit(x=out[:2], y=out[2], epochs=c.EPOCHS)
+
+  z = np.c_[out[0].reshape(len(out[0]), -1), out[1].reshape(len(out[1]), -1), out[2].reshape(len(out[2]), -1)]
+  np.random.shuffle(z)
+  x1 = z[:, :out[0].size//len(out[0])].reshape(out[0].shape)
+  x2 = z[:, out[0].size//len(out[0]):out[0].size//len(out[0]) + out[1].size//len(out[1])].reshape(out[1].shape)
+  y = z[:, out[0].size//len(out[0]) + out[1].size//len(out[1]):].reshape(out[2].shape)
+  model.fit(x=[x1, x2], y=y, epochs=c.EPOCHS, validation_split=0.1)
 
   print "Saving result..."
   model.save('models/' + username + '-mimic.h5')
 
 def train_distinguish(username):
   print "Creating Model..."
-  rnn_input = Input(shape = (c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 1))
+  rnn_input = Input(shape = (c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 2))
[…]

### 2017-05-14 tex/Paper/Paper.tex
started writeup

\documentclass{amsart}
\usepackage{amsmath, amssymb, amsthm}

\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\usepackage{enumitem}
\usepackage{multicol,caption}
\usepackage{graphicx}

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

\usepackage[margin=1in]{geometry}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily\scriptsize,
  mathescape
}

\usepackage{fancyhdr}

\title{SKAML: Simulating Known Actors with Machine Learning}
\author{Bryan~Cai, Yasyf~Mohamedali\\ \MakeLowercase{bcai, yasyf}}

\begin{document}

\begin{titlepage}
\centering
~
\vspace{7 cm}
\maketitle
~\\
May 14, 2017
\vfill

\end{titlepage}

\section{Abstract}
Rise of biometric identification \\
downside is hard to change if someone can mimic \\
one metric current systems use is to look at how users type \\
have a existing system from last year, show it is insecure \\
develop models to fool system and simulate how the user types \\
also build new model to distinguish between real user and other users \\
structure of paper \\

\begin{multicols*}{2}
\section{Introduction}

\section{Threat Model}

\section{Approach}
\subsection{Data Collection}

\subsection{Models}
For this project we trained several types of models. Our first model has the goal of mimicking how a user types. For each use when given a sequence of letters, the model outputs a sequence of delays between each consecutive pair of letters that mimics how the user would have typed those letters. It does this one pair at a time; the model takes as input $W$ letters preceding and $W$ letters following the pair we are predicting. For each of these $N$ letters, the model constructs a vector of length $V$, which represents the forward and backwards context in the word. Using these two vectors, one delay is produced. Iterating over every consecutive pair of letters gives the desired sequence of delays.

The next model, the distinguisher, tries to achieve the opposite effect; given a sequence of letters and timings, it tries to guess whether the sequence was typed by the user. This model takes as input a sequence of vectors, where each vector encodes what letter was typed, how long the key was held down for, and the delay from the last keypress.

\section{Implementation}

\subsection{Models}
The models were implemented in Python, using Keras with a TensorFlow backend. Characters were represented using one-hot vectors, and delays and hold times were measured in milliseconds. We first discuss the mimic model. This model takes two $W \times A$ matrices, where $W$ is the size of the context we consider and $A$ is the alphabet size. The first matrix represents the forward context, and the second matrix represents the backwards context. For example, if the word is "SECURITY," if we had a window size of 4 and we are trying to predict the delay between the "R" and the "I", the first matrix is the sequence of one-hot vectors representing ["C", "U", "R", "I"] and the second is the sequence of one-hot vectors representing ["R", "I", "T", "Y"]. If there are not enough letters, we pad the matrix with zero vectors. Each of these $W \times A$ matrices is fed through an RNN that produces the intermediate vector of length $V$. We then concatenate these two vectors and feed it through a fully connected layer with 50 nodes, and then then to a final output node. We used the mean absolute error as the loss function, and standard gradient descent as the optimizer.

The distinguisher model takes as input a matrix of size $L \times (A + 2)$, where $L$ is the maximum word length we allow, which is set to 15 but can be set higher in the future if necessary. Each row of the matrix consists of the one-hot vector of length $A$, with the keydown time and delay time appended. This is fed through one RNN layer, then through several dense layers, culminating in an final layer with 2 outputs and softmax activation.

\section{Conclusion}
Something here

\end{multicols*}
\end{document}

\grid

### 2017-05-15 src/collect/helpers/learn.py
Add frontend for testing model.

@@ -1,5 +1,13 @@
 from transform import ONE_HOT_SIZE, transform, str_to_idxs, chars_to_idxs
 import numpy as np
+import sys, os
+
+sys.path.append(os.path.abspath(os.path.join(os.pardir, 'train')))
+import predict
+
+def evaluate(username, password):
+  prob = predict.predict_distinguish(username, *transform({'words': [password]}))
+  return bool(np.argmax(prob) == 0), round(prob[0], 2)
 
 def one_hot_to_ind(x):
   return np.flatnonzero(x)[0]

### 2017-05-15 src/collect/routes.py

@@ -2,7 +2,7 @@ from flask import render_template, session, jsonify, request, send_file, redirec
 from app import app
 from helpers.mongo import db
 from helpers.transform import transform, encode_chars, filter_valid
-from helpers.learn import string_delay, chars_delay
+from helpers.learn import string_delay, chars_delay, evaluate
 import uuid, io, os
 import numpy as np
 
@@ -16,6 +16,10 @@ def preprocess_request():
 @app.route('/')
 def index_view():
   return render_template('index.html')
+
+@app.route('/login')
+def login_view():
+  return render_template('login.html')
 
 @app.route('/client')
 def client_view():
@@ -49,6 +53,11 @@ def chars_mean_view(id):
   obj = db.sessions.find_one({'id': id})
   delays = chars_delay(obj, request.json['word']['characters'])
   return jsonify({'delays': delays})
+
+@app.route('/evaluate', methods=['POST'])
+def evaluate_view():
+  success, likelihood = evaluate(request.json['username'], request.json['password'])
+  return jsonify({'success': success, 'likelihood': likelihood})
 
 @app.route('/encode', methods=['POST'])
 def encode_view():

### 2017-05-15 src/collect/static/js/login.js

@@ -1,0 +1,8 @@
+function evaluate(password) {
+  let username = $('#username').val();
+  post('/evaluate', {username, password}).then(resp =>
+    $('#response').html(`[${resp.likelihood}] ${resp.success ? 'Success!' : 'Failed :('}`)
+  );
+}
+
+monitor('#password', evaluate);

### 2017-05-15 src/train/functions.py

@@ -48,11 +48,7 @@ def filelist_to_mimic_data(filelist):
     y = np.append(y, out[2])
   return [x_1, x_2, y]
 
-def password_to_distinguish_data(filename):
-  X = np.load(filename)['X']
-  Y = np.load(filename)['Y']
-  Z = np.load(filename)['Z']
-
+def xyz_to_distinguish_data(X, Y, Z):
   output = []
   for i in range(len(X)):
     if len(X[i]) == 0:
@@ -62,7 +58,14 @@ def password_to_distinguish_data(filename):
     for j in range(len(Y[i])):
       a[c.MAX_WORD_SIZE - len(X[i]) + j + 1] = np.append(X[i][j + 1], [Z[i][j + 1]*0.01, Y[i][j]*0.01])
     output.append(a)
-  return output
+  return np.array(output)
+
+def password_to_distinguish_data(filename):
+  data = np.load(filename)
+  X = data['X']
+  Y = data['Y']
+  Z = data['Z']
+  return xyz_to_distinguish_data(X, Y, Z)
 
 def filelist_to_distinguish_data(filelist):
   x = np.zeros((0, c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 2))

### 2017-05-15 src/train/predict.py

@@ -1,32 +1,28 @@
-import sys
-import numpy as np
+import sys, os
 import constants as c
 import functions as f
-
+import numpy as np
 from keras.models import load_model
 
-
+MODEL_DIR = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'models')
 
 def predict_mimic(username, word):
   model = load_model('models/' + username + '-mimic.h5')
-  print model.predict(f.wordmatrix_to_input(c.matrix_dict[word])).flatten().tolist()
+  return model.predict(f.wordmatrix_to_input(c.matrix_dict[word])).flatten().tolist()
 
-
-def predict_mimic(username, word, timings, press_length):
-    a = np.zeros((c.MAX_WORD_SIZE, c.ALPHABET_SIZE + 2))
-    a[c.MAX_WORD_SIZE - len(word)] = np.append(word[0], [press_length[0], 0])
-    for j in range(len(timings)):
-      a[c.MAX_WORD_SIZE - len(word) + j + 1] = np.append(word[j + 1], [press_length[j + 1]*0.01, timings[j]*0.01])
-
-  model = load_model('models/' + username + '-distinguish.h5')
-  print model.predict(a)
-
+def predict_distinguish(username, word, timings, press_length):
+  model = os.path.join(MODEL_DIR, '{}-distinguish.h5'.format(username))
+  if not os.path.exists(model):
+    return np.array([0., 1.])
+  data = f.xyz_to_distinguish_data(word, timings, press_length)
+  model = load_model(model)
+  return model.predict(data).flatten()
 
 def main(args):
   if args[0] == 'mimic':
-    predict_mimic(args[1], args[2])
+    print predict_mimic(args[1], args[2])
   if args[0] == 'distinguish':
-    predict_distinguish(args[1], args[2], args[3], args[4])
+    print predict_distinguish(args[1], args[2], args[3], args[4])
 
 if __name__ == '__main__':
   main(sys.argv[1:])

### 2017-05-15 src/train/train.py

@@ -5,14 +5,10 @@ import constants as c
 import functions as f
 import numpy as np
 
-from keras.models import Sequential, Model
+from keras.models import Model
 from keras.layers import SimpleRNN
-from keras.layers import Activation, Dropout, Flatten, Dense, Concatenate, Masking, LeakyReLU
+from keras.layers import Dropout, Dense, Concatenate, Masking, LeakyReLU
 from keras.layers import Input
-from keras.optimizers import Nadam, SGD
-from keras.callbacks import Callback
-from keras import backend as K
-
 
 def train_mimic(username):
   print "Creating Model..."

### 2017-05-15 src/collect/helpers/learn.py
FIx relative path issue.

@@ -2,7 +2,7 @@ from transform import ONE_HOT_SIZE, transform, str_to_idxs, chars_to_idxs
 import numpy as np
 import sys, os
 
-sys.path.append(os.path.abspath(os.path.join(os.pardir, 'train')))
+sys.path.append(os.path.abspath(os.path.join(os.path.dirname(os.path.realpath(__file__)), os.pardir, os.pardir, 'train')))
 import predict
 
 def evaluate(username, password):

### 2017-05-15 src/collect/static/js/login.js
Add more feedback when submitting.

@@ -1,4 +1,5 @@
 function evaluate(password) {
+  $('#response').html('Submitting...');
   let username = $('#username').val();
   post('/evaluate', {username, password}).then(resp =>
     $('#response').html(`[${resp.likelihood}] ${resp.success ? 'Success!' : 'Failed :('}`)

### 2017-05-15 src/collect/helpers/learn.py
Fail fast on empty input.

@@ -6,6 +6,8 @@ sys.path.append(os.path.abspath(os.path.join(os.path.dirname(os.path.realpath(__
 import predict
 
 def evaluate(username, password):
+  if not password['characters']:
+    return False, 0
   prob = predict.predict_distinguish(username, *transform({'words': [password]}))
   return bool(np.argmax(prob) == 0), round(prob[0], 2)
 

### 2017-05-15 src/train/predict.py
Fix memory leak.

@@ -2,21 +2,28 @@ import sys, os
 import constants as c
 import functions as f
 import numpy as np
-from keras.models import load_model
+import keras.models
 
 MODEL_DIR = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'models')
+MODEL_CACHE = {}
+
+def distinquish_model(username):
+  return os.path.join(MODEL_DIR, '{}-distinguish.h5'.format(username))
+
+def load_distinquish_model(username):
+  if username not in MODEL_CACHE:
+    MODEL_CACHE[username] = keras.models.load_model(distinquish_model(username))
+  return MODEL_CACHE[username]
 
 def predict_mimic(username, word):
-  model = load_model('models/' + username + '-mimic.h5')
+  model = keras.models.load_model('models/' + username + '-mimic.h5')
   return model.predict(f.wordmatrix_to_input(c.matrix_dict[word])).flatten().tolist()
 
 def predict_distinguish(username, word, timings, press_length):
-  model = os.path.join(MODEL_DIR, '{}-distinguish.h5'.format(username))
-  if not os.path.exists(model):
+  if not os.path.exists(distinquish_model(username)):
     return np.array([0., 1.])
   data = f.xyz_to_distinguish_data(word, timings, press_length)
-  model = load_model(model)
-  return model.predict(data).flatten()
+  return load_distinquish_model(username).predict(data).flatten()
 
 def main(args):
   if args[0] == 'mimic':

### 2017-05-15 src/collect/helpers/learn.py
Add idxs_to_str transform helper.

@@ -1,4 +1,4 @@
-from transform import ONE_HOT_SIZE, transform, str_to_idxs, chars_to_idxs
+from transform import ONE_HOT_SIZE, transform, str_to_idxs, chars_to_idxs, one_hot_to_ind
 import numpy as np
 import sys, os
 
@@ -10,9 +10,6 @@ def evaluate(username, password):
     return False, 0
   prob = predict.predict_distinguish(username, *transform({'words': [password]}))
   return bool(np.argmax(prob) == 0), round(prob[0], 2)
-
-def one_hot_to_ind(x):
-  return np.flatnonzero(x)[0]
 
 def mean_delays(X, Y):
   means = np.zeros((ONE_HOT_SIZE, ONE_HOT_SIZE))

### 2017-05-15 src/collect/helpers/transform.py

@@ -9,6 +9,9 @@ HOLD_THRESHOLD = 150
 def str_to_idxs(s):
   return map(lambda c: ord(c.upper()) - FIRST_CODE, s)
 
+def idxs_to_str(idxs):
+  return ''.join(map(lambda i: chr(i + FIRST_CODE).lower(), idxs))
+
 def chars_to_idxs(chars):
   return [c['keyCode'] - FIRST_CODE for c in chars]
 
@@ -17,6 +20,9 @@ def encode_chars(chars):
 
 def filter_valid(obj):
   return [[c for c in w['characters'] if is_valid_char(c)] for w in obj['words'] if w['characters']]
+
+def one_hot_to_ind(x):
+  return np.flatnonzero(x)[0]
 
 def one_hot(char):
   one_hot = np.zeros(ONE_HOT_SIZE)

### 2017-05-15 tex/paper/paper.tex
Add intro and first half of models.

--- 2017-05-14 tex/Paper/Paper.tex
@@
 
+The past few years have seen several attempts to increase security in password-based authentication systems by adding secondary factors derived from biometric patterns in user behavior.
+Examples of this include Yang and Haddad's \textit{punchTimeAuth} \footnote{http://css.csail.mit.edu/6.858/2017/projects/yangjy-ddh.pdf} and the commercial product being developed by UnifyID \footnote{https://unify.id/}.
+However, there has not been much focus on the barrier this presents to attackers who are capable of mimicking their targets, particularly in the age of commodity cloud hardware and effective deep learning methods.
+
+We present an exploration into the pitfalls of relying on input-delay-based biometric data as a second factor for authentication, using \textit{punchTimeAuth} as our standard for comparison.
+We show that the model introduces a prohibively high number false negatives when exposed to real-world usage.
+Furthermore, we present serveral adversarial models which can successfully impersonate a user typing their password, trained on background typing data that need not include the password itself.
+In order to collect this data, we built two collection mediums: a Google Documents look-alike and an extension for Google Chrome.
+We collect which keys are pressed, the length of time each is held for, and the delay between each pair of keys.
+Finally, we present a novel neural model for attempting to distinguish users based on the information we collect, along with some conclusions and observations about this source of data as a second factor for security.
+
 \section{Threat Model}
+
+Our exploration focuses specifically on the systems which analyze the delays between a user's keypresses while she is typing her password.
+We assume that the system in question has been previously trained with multiple samples of the user's typing patterns.
+Our tests were against the seventh quantile-based \textit{punchTimeAuth}.
+We assume the role of an adversary which has managed to obtain the password of a user (such as through a database breach, phishing scam, or cross-site scripting exploit), and is attempting to gain access to a system employing the second factor of security described above.
+We further assume that the adversary has time to build tools as we did to collect typing data on their target.
+Importantly, we do not require the adversary to ever witness their target typing the password in question.
 
@@
 \subsection{Data Collection}
+
+In order to collect sufficient typing data from the users that agreed to participate in our exploration, we built two interactive tools.
+In both cases, we solicited complacent users by inviting them to use our applications, relying on their lack of careful inspection when receiving a link from someone they trust.
+
+The first is a Google Docs look-alike, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page.
+We overlayed a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with.
+We implemented a small client-side library in JavaScript which listens for the \texttt{KeyDown} and \texttt{KeyUp} DOM events emitted from the textbox, so as to record the length of time each key is held for and the delay between key presses, as well as the actual characters being typed.
+This data is stored in a local buffer and is periodically uploaded to our servers, where a a Flask app records the logged objects to a MongoDB instance, tagged with a unique identifier for the user in question.
 

### 2017-05-15 tex/paper/paper.tex
Add details on means model.

@@
 
+\textbf{TODO: ADD IMAGE OF GOOGLE DOCS FAKE}
+
+The second technique we developed for data collection is a key-logging Google Chrome extension.
+While the data quality from a document editor was vastly superior to the flow of data from casual bursts of typing in a browser, our models demanded as much data as we could possibly collect.
+Thus we augmented our corpus by creating an extension that injects a script into every web page, using the same library as before.
+We asked participants to install the extension and made them aware of the implications; our proof-of-concept was installed with consent but could just as easily be installed through less transparent means by a bad actor.
+
+\textbf{TODO: TALK ABOUT HOW MUCH DATA WE COLLECTED}
+
 \subsection{Models}
+\subsubsection{Means Model}
 For this project we trained several types of models.
-Our first model has the goal of mimicking how a user types.
+We first focused on the problem of tricking a security system into believing that we, as a hypothetical bad actor, were the original user, by simulating the delays that the original user would have in their password typing.
+
+To begin, we trained a simple means model to estimate the delay a specific user exhibits between any two characters, regardless of context.
+We simply used the average delay between a given pair of characters for the user in question, filling in missing data with a global mean.
+This model performed surprisingly well.
+
+\subsubsection{Neural Models}
+Our first neural model has the goal of mimicking how a user types, building on the simple means model and capturing additional context.
 For each use when given a sequence of letters, the model outputs a sequence of delays between each consecutive pair of letters that mimics how the user would have typed those letters.
@@
 
+We built a Python backend in Flask with an API to support our collection and processing.
+This included routines to receive JavaScript objects with \texttt{KeyCode}s and translate them to one-hot vectors which could be fed into our neural models.
+In order to aid with supervision of the collection process, we build several tools and dashboards to explore the data being collected.
+
+\textbf{TODO: ADD IMAGE OF DEBUGGING DASHBOARD}
+
 \subsection{Models}
-The models were implemented in Python, using Keras with a TensorFlow backend.
+\subsubsection{Means Model}
+Our means model for a given user $u$ was the result of a few simple NumPy operations, with the final \texttt{means} matrix defined as follows.
+\texttt{means} is an $N \times N$ matrix, where $N = |\mathcal{C}|$ is the cardinality of the set of characters that can appear in a string.
+For simplicity, we limited this set to lowercase letters, numbers, and punctuation.
+Element $(i, j)$ of \texttt{means} indicates the predicted user delay between typing character $i$ and character $j$.
+
+Let $y_u$ be the flattened length-$n$ vector of measurements $(c_1, c_2, \texttt{delay})$ taken for user $u$, where $\texttt{delay}$ is the delay between this particular instance of typing $c_1$ and $c_2$.
+Let $N_{c_1, c_2} = \texttt{count}(y_u : c_1 = i, c_2 = j)$.
+
+\[ \texttt{means}[i][j] :=
+  \begin{cases}
+      \frac{\sum_{y_u : c_1 = i, c_2 = j}{\texttt{delay}}}{N_{c_1, c_2}} & N_{c_1, c_2} > 0 \\
+      \frac{\sum_{\texttt{means} : N_{i, j} > 0}{\texttt{means}[i][j]}}{\texttt{count}(\texttt{means} : N_{i, j} > 0)} & N_{c_1, c_2} = 0 \\
+   \end{cases}
+\]
+
+\subsubsection{Neural Models}
+The neural models were implemented in Python, using Keras with a TensorFlow backend.
 Characters were represented using one-hot vectors, and delays and hold times were measured in milliseconds.
@@
 
+\section{Results}
+
+\textbf{TODO: RESULTS}
+
+\section{Discussion}
+
+\textbf{TODO: CHALLENGES}
+
 \section{Conclusion}
-Something here
+
+\textbf{TODO: CONCLUSION}
+
+\textbf{TODO: CITATIONS}
 

### 2017-05-15 tex/paper/paper.tex
Formatting and mean model results.

@@
 \documentclass{amsart}
-\usepackage{amsmath, amssymb, amsthm}
+\usepackage{amsmath, amssymb, amsthm, hyperref, enumitem, multicol, caption, graphicx}
 
-\usepackage [english]{babel}
-\usepackage [autostyle, english = american]{csquotes}
+\usepackage[english]{babel}
+\usepackage[autostyle, english=american]{csquotes}
+
+\setlength{\parskip}{\baselineskip}
+
 \MakeOuterQuote{"}
-\usepackage{enumitem}
-\usepackage{multicol,caption}
-\usepackage{graphicx}
 
@@
 \section{Abstract}
+\textbf{TODO: ABSTRACT}
 Rise of biometric identification \\
@@
 The past few years have seen several attempts to increase security in password-based authentication systems by adding secondary factors derived from biometric patterns in user behavior.
-Examples of this include Yang and Haddad's \textit{punchTimeAuth} \footnote{http://css.csail.mit.edu/6.858/2017/projects/yangjy-ddh.pdf} and the commercial product being developed by UnifyID \footnote{https://unify.id/}.
+Examples of this include Yang and Haddad's \texttt{punchTimeAuth} \footnote{http://css.csail.mit.edu/6.858/2017/projects/yangjy-ddh.pdf} and the commercial product being developed by UnifyID \footnote{https://unify.id}.
 However, there has not been much focus on the barrier this presents to attackers who are capable of mimicking their targets, particularly in the age of commodity cloud hardware and effective deep learning methods.
 
-We present an exploration into the pitfalls of relying on input-delay-based biometric data as a second factor for authentication, using \textit{punchTimeAuth} as our standard for comparison.
+We present an exploration into the pitfalls of relying on input-delay-based biometric data as a second factor for authentication, using \texttt{punchTimeAuth} as our standard for comparison.
 We show that the model introduces a prohibively high number false negatives when exposed to real-world usage.
@@
 
+All of the code for this paper can be found at \url{https://github.com/yasyf/skaml}.
+
 \section{Threat Model}
@@
 We assume that the system in question has been previously trained with multiple samples of the user's typing patterns.
-Our tests were against the seventh quantile-based \textit{punchTimeAuth}.
+Our tests were against the seventh quantile-based \texttt{punchTimeAuth}.
 We assume the role of an adversary which has managed to obtain the password of a user (such as through a database breach, phishing scam, or cross-site scripting exploit), and is attempting to gain access to a system employing the second factor of security described above.
@@
 
-The first is a Google Docs look-alike, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page.
+The first is a Google Docs look-alike \footnote{https://snarl.herokuapp.com}, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page.
 We overlayed a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with.
@@
 
-The second technique we developed for data collection is a key-logging Google Chrome extension.
+The second technique we developed for data collection is a key-logging Google Chrome extension \footnote{https://snarl.herokuapp.com/client}.
 While the data quality from a document editor was vastly superior to the flow of data from casual bursts of typing in a browser, our models demanded as much data as we could possibly collect.
@@
 This included routines to receive JavaScript objects with \texttt{KeyCode}s and translate them to one-hot vectors which could be fed into our neural models.
-In order to aid with supervision of the collection process, we build several tools and dashboards to explore the data being collected.
+In order to aid with supervision of the collection process, we built several tools and dashboards to explore the data being collected.
 
@@
 \section{Results}
+\subsection{Means Model}
+
+As we will discuss later, the laborious and manual process of training systems like \texttt{punchTimeAuth} left us in the difficult position of not having many options for automated testing.
+Thus, our testing efforts were the result of us randomly sampling words and attempting to have our model type them in the fashion of the training user.
+The same user would train the security system by using that word as their password for a new account, and we would inject JavaScript to simulate our predicted delays at a login screen.
+Using this method, our means model was able to successfully imitate several users 90\% of the time.
+
+\subsection{Neural Models}
 

### 2017-05-15 tex/paper/paper.tex
Add challenges.

@@
 
-\textbf{TODO: TALK ABOUT HOW MUCH DATA WE COLLECTED}
+The combined results of these two methods resulted in a data set of approximately $25000$ character pairs across several users.
 
@@
 Using this method, our means model was able to successfully imitate several users 90\% of the time.
+This result is somewhat surprising, given that we did not expect users to necessarily type in a document editor the same way they type a familiar password.
 
@@
 
-\textbf{TODO: CHALLENGES}
+We faced serval challenges in collecting data and implementing the models for this exploration.
+One of the largest barriers to rigorous results was the fact that the systems we attempted to break all require significant effort to train.
+Concretely, in order to evaluate an imitation of a user's typing of a specific password, that user must train the security system on how she types that password.
+This high barrier to the end user is a shortcoming of the string-specific model used in \texttt{punchTimeAuth}, and something we tried to address with our generalized neural distinguisher.
+However, as we discovered, simple typing timing and language context do not provide sufficient information to produce a generalized model of a user's biometric profile.
+
+Another particularly interesting challenge occured in the client-side data collection library we authored.
+Detecting lengths of key presses in addition to delays meant we could not simply listen for \texttt{KeyPress} events, and put us at the mercy of the JavaScript event loop scheduler.
+We spent nontrivial amount of time post-processing the stream of events we received to piece together the sequence of user key presses.
+
+On the data collection front, we experienced expected challenges including a lack of willing study participants, and foreign scripts interfering with our injected collection routines in the browser.
 

### 2017-05-15 tex/paper/paper.tex
Add images.
Add extra todo.
worked on paper, added sorted_timings

@@
 \documentclass{amsart}
-\usepackage{amsmath, amssymb, amsthm, hyperref, enumitem, multicol, caption, graphicx}
+\usepackage{amsmath, amssymb, amsthm, hyperref, enumitem, multicol, caption, graphicx, float}
 
@@
 \usepackage[autostyle, english=american]{csquotes}
+
+\graphicspath{ {images/} }
 
@@
 
-\title{SKAML: Simulating Known Actors with Machine Learning}
+\title{SNARL: Simulating Known Actors with Machine Learning}
 \author{Bryan~Cai, Yasyf~Mohamedali\\ \MakeLowercase{bcai, yasyf}}
@@
 ~\\
-May 14, 2017
+May 15, 2017
 \vfill
@@
 \section{Abstract}
-\textbf{TODO: ABSTRACT}
-Rise of biometric identification \\
-downside is hard to change if someone can mimic \\
-one metric current systems use is to look at how users type \\
-have a existing system from last year, show it is insecure \\
-develop models to fool system and simulate how the user types \\
-also build new model to distinguish between real user and other users \\
-structure of paper \\
+We present SNARL, a suite of tools that is able to simulate a user's typing pattern with the goal of exposing the  vulnerabilities of new biometric based identification techniques.
+Researchers have known for many years that password based verifcation systems are insecure, in part due to security holes in applications, and in part due to users (eg password reuse).
+In an effort to bolster security, some applications leverage additional data; we are particularly interested in the merits and drawbacks of biometric data.
+Biometric identifications schemes are in some aspects very secure, because a person can often be uniquely identified by some combination of biometric factors.
+On the other hand, if somehow this information were to be stolen, akin to a password being leaked, it is nearly impossible to change, since they are often either physical traits that exist from birth or habits developed over many years.
+Our paper demonstrates a system that is able to rapidly learn and simulate user password typing habits, and suggests that keypress timings should only be used as an inexpensive technique that does not significantly boost security.
 
@@
 
-\textbf{TODO: ADD IMAGE OF GOOGLE DOCS FAKE}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.4\textwidth]{gdocs}
+  \caption{Google Docs look-alike}
+\end{figure}
 
@@
 
-\textbf{TODO: ADD IMAGE OF DEBUGGING DASHBOARD}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.4\textwidth]{admin}
+  \caption{Data Debgging Dashboard}
+\end{figure}
 
@@
 
-\textbf{TODO: RESULTS}
+Our neural models for mimicking user input achieved a lower success rate on the task of imitating users to \texttt{punchTimeAuth}, succeeding on about 70\% of passwords.
+However, there are several possible explanations.
+We believe that the most likely reason is because the \texttt{punchTimeAuth} is based on deviation from the median for each keypress, which the means model learns more directly.
+Secondly, our neural model may be overfitting to the data, and we believe results would improve if there was more data, collected over a longer span of time, to train on.
+
+The distinguisher model had a validation accuracy of 80\% to 85\%, which indicates that there is an appreciable difference between how distinct users type; however, it is clearly also not enought to uniquely identify a user.
+Again, this analysis suffers from low sample size, as we were only able to analyze 4 user's typing habits.
 
@@
 
+\textbf{TODO: KEYBOARD DISTANCE THING}
+
 \section{Conclusion}
 
-\textbf{TODO: CONCLUSION}
-
-\textbf{TODO: CITATIONS}
+SNARL has demonstrated that timing-enhanced password authentication has approximately the same level of security as a password-only scheme, given 10,000 to 15,000 characters of data per user, which is about 4 pages of typed words.
+We successfully defeated the scheme presented in \texttt{punchTimeAuth} using both a very simple means model and a neural model.
+However, our distinguisher models show that there is differentiation in user typing habits, and typing patterns could be aggregated with other data to effectively enhance security.
 
 \end{multicols*}
+
+\begin{thebibliography}{99}
+
+\bibitem{LSTM}  Zachary C. Lipton, David C. Kale, Charles Elkan, Randall Wetzell {\em Learning to Diagnose with LSTM Recurrent
+Neural Networks}, arXiv:1511.03677, [2016].
+\end{thebibliography}
+
+\end{document}
+
 \end{document}

### 2017-05-15 tex/paper/paper.tex
Add bibliography.

@@
-\documentclass{amsart}
-\usepackage{amsmath, amssymb, amsthm, hyperref, enumitem, multicol, caption, graphicx, float}
+\documentclass[9pt,journal]{IEEEtran}
+\usepackage{graphicx,float,amsmath,amssymb,url,subcaption,array,fancyhdr}
 
@@
 \usepackage[autostyle, english=american]{csquotes}
+\usepackage[unicode]{hyperref}
 
@@
 
+\usepackage[backend=biber]{biblatex}
+\bibliography{paper}
+
 \MakeOuterQuote{"}
-
-\newenvironment{Figure}
-  {\par\medskip\noindent\minipage{\linewidth}}
-  {\endminipage\par\medskip}
 
@@
 
-\usepackage{fancyhdr}
-
-\title{SNARL: Simulating Known Actors with Machine Learning}
-\author{Bryan~Cai, Yasyf~Mohamedali\\ \MakeLowercase{bcai, yasyf}}
+\title{SNARL:\\Simulating Known Actors with Machine Learning}
+\author{\IEEEauthorblockN{Bryan Cai, Yasyf Mohamedali}\\\IEEEauthorblockA{\{bcai, yasyf\}@mit.edu}}
 
@@
 
-\begin{titlepage}
-\centering
-~
-\vspace{7 cm}
 \maketitle
-~\\
-May 15, 2017
-\vfill
-
-\end{titlepage}
 
 \section{Abstract}
+
 We present SNARL, a suite of tools that is able to simulate a user's typing pattern with the goal of exposing the  vulnerabilities of new biometric based identification techniques.
@@
 
-\begin{multicols*}{2}
 \section{Introduction}
@@
 The past few years have seen several attempts to increase security in password-based authentication systems by adding secondary factors derived from biometric patterns in user behavior.
-Examples of this include Yang and Haddad's \texttt{punchTimeAuth} \footnote{http://css.csail.mit.edu/6.858/2017/projects/yangjy-ddh.pdf} and the commercial product being developed by UnifyID \footnote{https://unify.id}.
+Examples of this include Yang and Haddad's \texttt{punchTimeAuth} \cite{punchtimeauth} and the commercial product being developed by UnifyID \cite{unifyid}.
 However, there has not been much focus on the barrier this presents to attackers who are capable of mimicking their targets, particularly in the age of commodity cloud hardware and effective deep learning methods.
@@
 
-All of the code for this paper can be found at \url{https://github.com/yasyf/skaml}.
+The code for the systems described in this paper can be found at \url{https://github.com/yasyf/snarl}.
 
@@
 
-The first is a Google Docs look-alike \footnote{https://snarl.herokuapp.com}, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page.
+The first is a Google Docs look-alike \cite{gdocs}, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page.
 We overlayed a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with.
@@
 
-The second technique we developed for data collection is a key-logging Google Chrome extension \footnote{https://snarl.herokuapp.com/client}.
+The second technique we developed for data collection is a key-logging Google Chrome extension \cite{extension}.
 While the data quality from a document editor was vastly superior to the flow of data from casual bursts of typing in a browser, our models demanded as much data as we could possibly collect.
@@
 The distinguisher model had a validation accuracy of 80\% to 85\%, which indicates that there is an appreciable difference between how distinct users type; however, it is clearly also not enought to uniquely identify a user.
-Again, this analysis suffers from low sample size, as we were only able to analyze 4 user's typing habits.
+Again, this analysis suffers from low sample size, as we were only able to analyze four user's typing habits.
 
@@
 
-\end{multicols*}
-
-\begin{thebibliography}{99}
-
-\bibitem{LSTM}  Zachary C. Lipton, David C. Kale, Charles Elkan, Randall Wetzell {\em Learning to Diagnose with LSTM Recurrent
-Neural Networks}, arXiv:1511.03677, [2016].
-\end{thebibliography}
+\pagebreak
+\printbibliography
 
 \end{document}
-
-\end{document}
-
-\grid

### 2017-05-15 src/train/analysis.py
added analysis.py

@@ -1,0 +1,114 @@
+import sys
+import glob
+import numpy as np
+import operator
+
+FIRST_CODE = 48
+LAST_CODE = 90
+ONE_HOT_SIZE = LAST_CODE - FIRST_CODE + 1
+TIME_DIFF_THRESHOLD = 300
+HOLD_THRESHOLD = 150
+
+type_dict = {}
+type_dict['a'] = 1
+type_dict['b'] = 4
+type_dict['c'] = 3
+type_dict['d'] = 3
+type_dict['e'] = 3
+type_dict['f'] = 4
+type_dict['g'] = 4
+type_dict['h'] = 5
+type_dict['i'] = 6
+type_dict['j'] = 5
+type_dict['k'] = 6
+type_dict['l'] = 7
+type_dict['m'] = 6
+type_dict['n'] = 5
+type_dict['o'] = 7
+type_dict['p'] = 8
+type_dict['q'] = 1
+type_dict['r'] = 4
+type_dict['s'] = 2
+type_dict['t'] = 4
+type_dict['u'] = 5
+type_dict['v'] = 4
+type_dict['w'] = 2
+type_dict['x'] = 2
+type_dict['y'] = 5
+type_dict['z'] = 1
+
+
+def idxs_to_str(idxs):
+  return ''.join(map(lambda i: chr(i + FIRST_CODE).lower(), idxs))
+
+def idx_to_char(idx):
+  return chr(idx + FIRST_CODE).lower()
+
+def one_hot_to_ind(x):
+  return np.flatnonzero(x)[0]
+
+
+def mean_delays(X, Y):
+  means = np.zeros((ONE_HOT_SIZE, ONE_HOT_SIZE))
+  counts = np.zeros((ONE_HOT_SIZE, ONE_HOT_SIZE))
+
+  for i, word in enumerate(X):
+    for j, char in enumerate(word):
+      if j == 0:
+        continue
+      c1 = one_hot_to_ind(word[j - 1])
+      c2 = one_hot_to_ind(char)
+      means[c1][c2] += Y[i][j - 1]
+      counts[c1][c2] += 1
+
+  counts[np.where(counts == 0)] = 1
+  means /= counts
+  mean = means.ravel()[np.flatnonzero(means)].mean()
+  means[np.where(means == 0)] = mean
+  return means
+
+def user_mean_delays(username):
[…]

### 2017-05-15 tex/paper/paper.tex
Add data for keyboard distances.

@@
 We overlayed a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with.
+
 We implemented a small client-side library in JavaScript which listens for the \texttt{KeyDown} and \texttt{KeyUp} DOM events emitted from the textbox, so as to record the length of time each key is held for and the delay between key presses, as well as the actual characters being typed.
@@
 The first matrix represents the forward context, and the second matrix represents the backwards context.
+
 For example, if the word is "SECURITY," if we had a window size of 4 and we are trying to predict the delay between the "R" and the "I", the first matrix is the sequence of one-hot vectors representing ["C", "U", "R", "I"] and the second is the sequence of one-hot vectors representing ["R", "I", "T", "Y"].
@@
 We then concatenate these two vectors and feed it through a fully connected layer with 50 nodes, and then then to a final output node.
+
 We used the mean absolute error as the loss function, and standard gradient descent as the optimizer.
@@
 On the data collection front, we experienced expected challenges including a lack of willing study participants, and foreign scripts interfering with our injected collection routines in the browser.
+The latter resulted in the data collected from our Chrome extension being very noisy and hard to use.
 
-\textbf{TODO: KEYBOARD DISTANCE THING}
+As part of our analysis of user typing data, we made some interesting observations with regards to the delays between typing keys on a standard QWERTY keyboard.
+Our initial hypothesis was that keys which are farther apart on the standard keyboard would experience the greatest delay.
+However, as seen in Figure \ref{fig:keyboard}, this is not quite the case.
+
+Instead, we see a pattern where keys that are typed by the same finger (on either side of the keyboard) follow each other in quick succession, with the distance between keys not rendering much information.
+The exception to this is the peculiarity of typing the same key multiple times.
+It appears that users consistently slow down when repeating a key.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.4\textwidth]{keyboard}
+  \caption{Keyboard Distance vs Mean Delay}
+  \label{fig:keyboard}
+\end{figure}
+
+\section{Future Work}
+
+Though we have shown that there is significant differentiation between user's typing patterns.
 

### 2017-05-15 data/keyboard_distance.py

@@ -1,0 +1,9 @@
+import numpy as np
+
+keyboard_cartesian = {'q': {'x':0, 'y':0}, 'w': {'x':1, 'y':0}, 'e': {'x':2, 'y':0}, 'r': {'x':3, 'y':0}, 't': {'x':4, 'y':0}, 'y': {'x':5, 'y':0}, 'u': {'x':6, 'y':0}, 'i': {'x':7, 'y':0}, 'o': {'x':8, 'y':0}, 'p': {'x':9, 'y':0}, 'a': {'x':0, 'y':1},'z': {'x':0, 'y':2},'s': {'x':1, 'y':1},'x': {'x':1, 'y':2},'d': {'x':2, 'y':1},'c': {'x':2, 'y':2}, 'f': {'x':3, 'y':1}, 'b': {'x':4, 'y':2}, 'm': {'x':5, 'y':2}, 'j': {'x':6, 'y':1}, 'g': {'x':4, 'y':1}, 'h': {'x':5, 'y':1}, 'j': {'x':6, 'y':1}, 'k': {'x':7, 'y':1}, 'l': {'x':8, 'y':1}, 'v': {'x':3, 'y':2}, 'n': {'x':5, 'y':2}, }
+
+def keyboard_distance(a, b):
+    X = keyboard_cartesian[a]['x'] - keyboard_cartesian[b]['x']
+    Y = keyboard_cartesian[a]['y'] - keyboard_cartesian[b]['y']
+    return np.sqrt(np.power(X, 2) + np.power(Y, 2))
+

### 2017-05-15 data/sorted_timings.py

@@ -1,0 +1,1 @@
+SORTED_TIMINGS = [(('i', 'o'), 52.294117647058826), (('o', 'r'), 53.349999999999454), (('a', 'm'), 55.555555555555557), (('t', 'a'), 60.904761904762253), (('e', 'r'), 62.032608695652016), (('n', 'e'), 62.183673469385383), (('o', 'n'), 62.707317073170735), (('a', 'l'), 63.641509433966384), (('w', 'e'), 64.615384615380137), (('p', 'r'), 67.818181818187114), (('h', 'e'), 68.147540983605182), (('k', 'e'), 68.950000000002547), (('t', 's'), 70.099999999999994), (('t', 'e'), 70.424999999998548), (('l', 'i'), 72.431818181818187), (('o', 'w'), 73.0), (('d', 'o'), 73.0), (('n', 'd'), 73.219512195121951), (('u', 'l'), 74.473684210529385), (('i', 'n'), 76.310344827586206), (('m', 'e'), 76.862745098041501), (('r', 'e'), 77.098591549294341), (('c', 'a'), 77.107142857142861), (('t', 'o'), 78.061538461542042), (('c', 'h'), 78.540540540540931), (('w', 'h'), 79.549999999999997), (('l', 'e'), 80.166666666666671), (('a', 'r'), 80.214285714286063), (('c', 'o'), 80.230769230769226), (('n', 'o'), 80.6875), (('r', 'o'), 81.78431372548792), (('n', 's'), 81.838709677419359), (('c', 'k'), 82.340425531913496), (('r', 'a'), 82.446808510638292), (('n', 'g'), 82.859999999999999), (('e', 's'), 83.019999999995932), (('a', 'n'), 83.095238095238102), (('h', 'a'), 83.409090909090907), (('p', 'o'), 83.571428571428569), (('s', 'o'), 84.904761904767454), (('h', 'i'), 84.9375), (('y', 's'), 85.0), (('u', 's'), 85.240000000002325), (('w', 'o'), 85.666666666666671), (('t', 'w'), 86.076923076918604), (('o', 'p'), 86.450000000001452), (('k', 's'), 86.909090909090253), (('h', 'o'), 88.280000000000001), (('o', 'f'), 88.354838709666154), (('p', 'e'), 88.76190476190061), (('o', 'u'), 89.803030303030297), (('u', 't'), 90.519999999999996), (('b', 'o'), 90.821428571428569), (('g', 'o'), 91.23076923076922
[…]

### 2017-05-15 src/train/analysis.py
Quick fix.

@@ -87,8 +87,6 @@ def user_mean_delays(username):
 
   counts[np.where(counts == 0)] = 1
   means /= counts
-  mean = means.ravel()[np.flatnonzero(means)].mean()
-  # means[np.where(means == 0)] = mean
   return means, counts
 
 def sort_timings(username):

### 2017-05-15 tex/paper/paper.tex
Add Future Work.

@@
 
-Though we have shown that there is significant differentiation between user's typing patterns.
+We have shown that there is significant differentiation between user's typing patterns, as evidenced by the results of our distinguisher model.
+However, it is not clear to the authors that there exists sufficient entropy in this data to uniquely identify a user in a large system.
+Certainly, timing delays and key hold times do not render a model that should be used as a second factor alone.
+We would like to explore how the signal from such a model can be used a heuristic for other biometric factors, as well as whether or not such signals could be aggregated to provide a secure authenication system.
 
@@
 
-\pagebreak
 \printbibliography

### 2017-05-15 tex/paper/paper.tex
Typos.

@@
 In an effort to bolster security, some applications leverage additional data; we are particularly interested in the merits and drawbacks of biometric data.
-Biometric identifications schemes are in some aspects very secure, because a person can often be uniquely identified by some combination of biometric factors.
+Biometric identification schemes are in some aspects very secure, because a person can often be uniquely identified by some combination of biometric factors.
 On the other hand, if somehow this information were to be stolen, akin to a password being leaked, it is nearly impossible to change, since they are often either physical traits that exist from birth or habits developed over many years.
@@
 Detecting lengths of key presses in addition to delays meant we could not simply listen for \texttt{KeyPress} events, and put us at the mercy of the JavaScript event loop scheduler.
-We spent nontrivial amount of time post-processing the stream of events we received to piece together the sequence of user key presses.
+We spent a nontrivial amount of time post-processing the stream of events we received to piece together the sequence of user key presses.
 

### 2017-05-15 tex/paper/paper.tex
Final paper and README.

@@
 We present SNARL, a suite of tools that is able to simulate a user's typing pattern with the goal of exposing the vulnerabilities of new biometric based identification techniques.
-Researchers have known for many years that password based verifcation systems are insecure, in part due to security holes in applications, and in part due to users (eg password reuse).
+Researchers have known for many years that password based verification systems are insecure, in part due to security holes in applications, and in part due to users (e.g.
+password reuse).
 In an effort to bolster security, some applications leverage additional data; we are particularly interested in the merits and drawbacks of biometric data.
@@
 We present an exploration into the pitfalls of relying on input-delay-based biometric data as a second factor for authentication, using \texttt{punchTimeAuth} as our standard for comparison.
-We show that the model introduces a prohibively high number false negatives when exposed to real-world usage.
-Furthermore, we present serveral adversarial models which can successfully impersonate a user typing their password, trained on background typing data that need not include the password itself.
+We show that the model introduces a prohibitively high number false negatives when exposed to real-world usage.
+Furthermore, we present several adversarial models which can successfully impersonate a user typing their password, trained on background typing data that need not include the password itself.
 In order to collect this data, we built two collection mediums: a Google Documents look-alike and an extension for Google Chrome.
@@
 The first is a Google Docs look-alike \cite{gdocs}, which imitates a well-known service in a phishing-style attempt to convince a complacent user to type on the page.
-We overlayed a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with.
+We overlaid a text box on a webpage containing the CSS from a Google Doc we created, allowing the user to type as if this were the application they are so familiar with.
 
@@
   \includegraphics[width=0.4\textwidth]{admin}
-  \caption{Data Debgging Dashboard}
+  \caption{Data Debugging Dashboard}
 \end{figure}
@@
 
-The distinguisher model had a validation accuracy of 80\% to 85\%, which indicates that there is an appreciable difference between how distinct users type; however, it is clearly also not enought to uniquely identify a user.
+The distinguisher model had a validation accuracy of 80\% to 85\%, which indicates that there is an appreciable difference between how distinct users type; however, it is clearly also not enough to uniquely identify a user.
 Again, this analysis suffers from low sample size, as we were only able to analyze four user's typing habits.
@@
 
-We faced serval challenges in collecting data and implementing the models for this exploration.
+We faced several challenges in collecting data and implementing the models for this exploration.
 One of the largest barriers to rigorous results was the fact that the systems we attempted to break all require significant effort to train.
@@
 
-Another particularly interesting challenge occured in the client-side data collection library we authored.
+Another particularly interesting challenge occurred in the client-side data collection library we authored.
 Detecting lengths of key presses in addition to delays meant we could not simply listen for \texttt{KeyPress} events, and put us at the mercy of the JavaScript event loop scheduler.
@@
 Certainly, timing delays and key hold times do not render a model that should be used as a second factor alone.
-We would like to explore how the signal from such a model can be used a heuristic for other biometric factors, as well as whether or not such signals could be aggregated to provide a secure authenication system.
+We would like to explore how the signal from such a model can be used a heuristic for other biometric factors, as well as whether or not such signals could be aggregated to provide a secure authentication system.
 

### 2017-05-15 tex/paper/paper.tex
Fix typo.

@@
 We present an exploration into the pitfalls of relying on input-delay-based biometric data as a second factor for authentication, using \texttt{punchTimeAuth} as our standard for comparison.
-We show that the model introduces a prohibitively high number false negatives when exposed to real-world usage.
+We show that the model introduces a prohibitively high number of false negatives when exposed to real-world usage.
 Furthermore, we present several adversarial models which can successfully impersonate a user typing their password, trained on background typing data that need not include the password itself.
@@
 We implemented a small client-side library in JavaScript which listens for the \texttt{KeyDown} and \texttt{KeyUp} DOM events emitted from the textbox, so as to record the length of time each key is held for and the delay between key presses, as well as the actual characters being typed.
-This data is stored in a local buffer and is periodically uploaded to our servers, where a a Flask app records the logged objects to a MongoDB instance, tagged with a unique identifier for the user in question.
+This data is stored in a local buffer and is periodically uploaded to our servers, where a Flask app records the logged objects to a MongoDB instance, tagged with a unique identifier for the user in question.
 
